Adopting agile software development in the large organizations: A systematic literature review

### 2014-06-05 journal/article.tex
Editing: Success factors

\begin{figure}[!b]
  \begin{center}
    \includegraphics{graphics/challenges_summary.pdf}
    \caption{Overview of challenges in agile transformation}
    \label{fig:challenges_summary}
  \end{center}
\end{figure}

@@

* What is our standpoint on recommendations that experience reports give, but
  which were not necessarily tried in the organization?

* Some success factors are just calculated decisions that were made because
  the organization saw them as the best way to proceed. The question whether
  the decision really were critical for success is not proven.

* Some success factors are compiled from ``what we learned'' or ``advice for
  others'' lists. We considered whether the advice was something the
  organization had tried in practice.

* For instance, implementing continuous integration and automated builds was not
  explicitly stated as a factor contributing to the success of the
  transformation, although it is unquestionable that such systems are critical
  for maintaining quality and enabling frequent releases.

Agile methods come as new ways of working to many in the organization. In order
to get a good start in the transformation the ideas of the new methods need to
be explained thoroughly. Training sessions are good starting points, but teams
should be accompanied by coaching for a longer time to ensure that the new
practices are learned and applied correctly in practice. Table
\ref{table:success_training} lists references that highlight training and
coaching as success factors.

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Providing training on agile methods  &
                P3, P6, P11, P14, P16, P30, P37, P46 \\
        Coaching teams as they learn by doing  &
                P3, P6, P8, P9 P16, P17, P18, P29,
                P30, P33, P42, P44, P47, P48  \\
        \bottomrule
    \end{tabular}
    \caption{Training and coaching presented as success factors}
    \label{table:success_training}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Have a pilot project at start  &
                P3, P9, P14, P17, P31, P36, P38, P39, P47  \\
        Gather insights from pilot projects  &
                P8, P22, P27, P40, P45  \\
        \bottomrule
    \end{tabular}
    \caption{Piloting the agile model as a success factor}
    \label{table:success_pilots}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Customizing the agile model  &
                P8, P10, P11, P29, P31, P40, P41, P43, P45, P49, P51  \\
        Conformity to a single agile model  &
                P8, P11, P12, P16, P32, P43  \\
        Mapping to the old model eases adaptation  &
                P14, P29, P44, P46, P48  \\
        Keeping the new model simple  &
                P5, P10, P16, P40  \\
        \bottomrule
    \end{tabular}
    \caption{Recommendations for choosing the agile model}
    \label{table:success_choosemodel}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Pay attention to the Product Owner role  &
                P12, P14, P16, P24, P30, P33, P39, P46  \\
        Pay attention to requirements management  &
                P5, P11, P17, P33, P48  \\
        \bottomrule
    \end{tabular}
    \caption{Careful implementation of requirements management seen as a
             success factor}
    \label{table:success_requirements}
\end{table}

@@

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Have management support  &
                P8, P11, P16, P18, P27, P31, P33, P36,
                P43, P44, P46, P47, P49  \\
        Visible management support encourages employees  &
                P9, P11, P24, P40  \\
        Educate management on agile methods  &
                P6, P8, P9, P11, P16, P29, P35, P46, P47  \\
        \bottomrule
    \end{tabular}
    \caption{Success factors relating to management support for agile}
    \label{table:success_management}
\end{table}

\subsubsection{Urgency and commitment to change}

To make a large organization change the direction of the change needs to be
communicated clearly. Articulating urgency at start will help getting the change
under way [P49]. Feedback of changes should certainly be listened to, but in the
end it must be made clear that the old model can not be returned to [P22].
For a case where the organization was changed all at once it was reported that
the magnitude of change helped created the impression that the change was non
negotiable [P11]. Firstly, as it was evident that a large change was to happen
people felt encouragement and permission to move on from the old way, and
secondly, the urgency eliminated wasteful discussions on whether Scrum was a good
model or not [P11].
When the organization culture is ingrown he change vision must constantly be
reminded of, and each step towards the new model consider a victory [P48].

A large change will inevitably require strong commitment. The agile model is
introduced because of problems in the old model, and therefore there will be
organizational issues uncovered during the transformation [P10]. People must not
be demoralized when facing challenges, and the determination to change must be
maintained [P8, P10]. It is not the agile model that has flaws, but it is
merely exposing problems in the organization [P10].
Ryan and Scudiere [P43] describe that management commitment was showing as
strong focus on certain agile practices that had been chosen as non negotiable,
and constant assessment that the practices work. The expectations were clearly
communicated to the teams, and constant assessment made it clear that change is
desired [P43].
A strong commitment from management will assure teams that the change is the
right thing [P11].

Spayd [P49] describes that senior management pushed hard on a mandate to have
deliveries every 90 days. The mandate made change necessary, and while the
strong pressure did not promote agile practices in every case the drive for
change was perceived good in general [P49].

\subsubsection{Have a change leading coalition}

Organizing a large number of people requires some management and leadership.
Similarly, transforming the way of working of a large group requires coordination
and leadership [P42, P31]. In addition to the leadership provided by coaches,
specific change leaders were also mentioned. Cases indicated the importance of
having spokespersons for the change [P3, P4, P31]. Cowan [P11] describes how one
person was strongly driving the transformation, and made an indisputable
contribution for transforming the organization. Also Maples [P31] describes how
the change and agile adoption was guided by one ``counselor'' [P31]. Other cases
described that the change was lead by a competent roll-out team, which had
representatives from all parts of the organization [P16, P33]. Finally, the
responsibility of line and project managers to act as change leaders was
highlighted [P18].

The formation and influence of agile communities was reported to have a
significant impact on transformation.
The emergence of an agile community was reported as a success factor in the
transformation [P3]. A community was also seen as indispensable as it has power
to overcome impediments that would be too large for individuals to affect [P47].
The agile communities achieved to raise awareness of agile methods in the
organization [P42, P41, P47], and spawned eager followers who spread the word
even further [P12].

A factor in achieving change was creating alignment towards the common goal of
introducing a new development method. It was seen as an important factor that
all levels in the organization speak the same language and accept the change
[P18, P31]. Alignment was built by promoting success stories and gathering lists
of problems to tackle [P42, P46]. In one case complete alignment between teams
and within management was considered as necessary to use the agile model in a
large context [P43]. Another case highlighted creating and applying a structured
roll-out process to uniformly introduce a large number of teams to agile [P8].

@@

@@

@@

Communicating the goals of the transformation was highlighted in a some studies.
Having a clear message of expectations helped to remove confusion and make
people understand the purpose of the transformation [P43, P48]. The motivation
to change can be increased by having a simple proposal on how to reach the
desired outcomes [P40].

%         Emphasizing principles over mechanics  &
%                 P1, P16, P32, P42, P46, P48  \\

In a number of studies it was described that during transformation the
principles of agile should be emphasized over practices and simple mechanics
[P46, P48]. When people understand the agile values they will also understand
why the change is being done and feel motivated [P1, P16, P42].
The people centric nature of agile development should be communicated correctly.
McDowell and Dourambeis [P32] describe how the organization launched a series of
communications events especially designed to emphasize the reasons behind the
agile practices.

% ??
Especially inexperienced coaches and Scrum masters made mistakes in focusing too
much on the implementation of practices [P23, P30].

@@

Many cases highlighted how people were engaged broadly in the organization.
One of the lessons learned presented was that it is important to involve all
stakeholders to gain acceptance in the transformation [P4, P31]. The transition
team made an effort to engage people by both inviting to give feedback online
and holding an extensive number of feedback meetings [P6, P22, P16]
Being inclusive towards everyone was seen as one of the key success factors in
the transformation [P16]. Inclusiveness will encourage people to participate and
use the new model visibly [P16].

\subsubsection{Enable autonomy}

@@

Roche and Vasquez-McCall [P41] describe how prescribing the agile methods to use
lead only so-far in the transformation. The effectiveness of teaching and
communicating the transformation started to decline. To enable the
transformation to still proceed, the an organization-wide challenge was created
where teams would independently develop and showcase the best agile practices.
As a result the ownership of the methods was transferred to teams, and the new
model gained a secure foothold. [P41]

@@

An interesting success factor was the absence of a top-down mandate. Atlas [P3]
describes that the use of Scrum was spreading because teams were both allowed to
use and enabled to learn the method. The transformation itself was agile when
people felt empowerment in making the decision to adopt. The incentive to change
was created when teams learned about agile methods, and perceived that a change
would be beneficial [P3].
The absence of mandate granted genuine support for the model on the grass roots
level, which was a necessity for the process to work [P6].
It was also thought that proceeding with a top-down mandate would have made
teams use a uniform process [P41]. This would have been sub-optimal, as it was
important that the practices were tailored for each team and project [P41].

A few organizations had already some structures in place that were similar to
agile, which made the transformation easier.
For instance, a previous organizational model based on small and autonomous
teams strongly aided the adoption [P3].
Another case described the original on-demand delivery model a natural fit for
agile, and the transformation was presented as a return to core values instead
of a remodeling [P16].
% The agile culture must also be maintained in each step of the transformation
% [P31]

\subsubsection{People factors}

The transformation did not entirely rely on choices in technology and
management, but also different people factors were given as basis of success.

@@

@@

>>>>

\begin{figure}[!b]
  \begin{center}
    \includegraphics{graphics/challenges_summary.pdf}
    \caption{Overview of challenges in agile transformations}
    \label{fig:challenges_summary}
  \end{center}
\end{figure}

@@

\begin{figure}[!b]
  \begin{center}
    \includegraphics[width=1\textwidth]{graphics/success_summary.pdf}
    \caption{Overview of success factors in agile transformations}
    \label{fig:success_summary}
  \end{center}
\end{figure}

Figure \ref{fig:success_summary} summarizes success factors evident in the
primary studies. The success factors are organized into ten categories within
three themes, which are elaborated in this section. The first theme relates to
management and leadership in the transformation. The second theme presents
success factors that relate to finding a suitable agile model for the
organization. The last theme includes success factors that are realized on the
level of development teams.

The discovered success factors did not exhibit strong differences in
significance in respect to each other. Three categories of success factors can
be considered of higher importance: management support, training and coaching,
and choosing the agile model carefully. The remaining success factors should be
considered having even significance.

% * What is our standpoint on recommendations that experience reports give, but
%   which were not necessarily tried in the organization?
% 
% * Some success factors are just calculated decisions that were made because
%   the organization saw them as the best way to proceed. The question whether
%   the decision really were critical for success is not proven. 
% 
% * Some success factors are compiled from ``what we learned'' or ``advice for
%   others'' lists. We considered whether the advice was something the
%   organization had tried in practice.
% 
% * For instance, implementing continuous integration and automated builds was not
%   explicitly stated as a factor contributing to the success of the
%   transformation, although it is unquestionable that such systems are critical
%   for maintaining quality and enabling frequent releases.

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.41\textwidth}
                     >{\raggedright\arraybackslash}p{0.51\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Have management support  &
                P8, P11, P16, P18, P27, P31, P33, P36,
                P43, P44, P46, P47, P49  \\
        Visible management support encourages employees  &
                P9, P11, P24, P40  \\
        Educate management on agile methods  &
                P6, P8, P9, P11, P16, P29, P35, P46, P47  \\
        \bottomrule
    \end{tabular}
    \caption{Success factors relating to management support for agile}
    \label{table:success_management}
\end{table}

\subsubsection{Commitment to change}

To make a large organization change the commitment to change must be made clear.
People should be made to understand that there is no return to the old model.
If and when the changes uncover problems they must not be allowed to set back
the transformation. Table \ref{table:success_commitment} lists sources which
present commitment to change as a success factor.

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Make it understood that the change is non-negotiable  &
                P11, P22, P48, P49  \\
        Commitment to change  &
                P8, P10, P43  \\
        \bottomrule
    \end{tabular}
    \caption{Commitment to change as a success factor}
    \label{table:success_commitment}
\end{table}

Articulating urgency at start will help getting the change under way [P49].
Feedback of changes should certainly be listened to, but in the end it must be
made clear that the old model can not be returned to [P22].
For a case where the organization was changed all at once it was reported that
the magnitude of change helped created the impression that the change was non
negotiable [P11]. Firstly, as it was evident that a large change was to happen
people felt encouragement and permission to move on from the old way, and
secondly, the urgency eliminated wasteful discussions on whether Scrum was a
good model or not [P11].
When the organization culture is ingrown he change vision must constantly be
reminded of, and each step towards the new model consider a victory [P48].

Transformation can be facilitated by creating mechanisms that force change.
Spayd [P49] describes that senior management pushed hard on a mandate to have
deliveries every 90 days. The mandate made change necessary, and while the
strong pressure did not promote agile practices in every case, the drive for
change was perceived good in general [P49].

A large change will inevitably require strong commitment, but problems in the
transformation can put the commitment to test. The agile model is introduced
because of problems in the old model, and therefore there will be organizational
issues uncovered during the transformation [P10]. People must not be demoralized
when facing challenges, and the determination to change must be maintained [P8,
P10]. It is not the agile model that has flaws, but it is merely exposing
problems in the organization [P10].

Ryan and Scudiere [P43] describe that management commitment was showing as
strong focus on certain agile practices that had been chosen as non negotiable,
and constant assessment that the practices work. The expectations were clearly
communicated to the teams, and constant assessment made it clear that change is
desired [P43].
A strong commitment from management will assure teams that the change is the
right thing [P11].

\subsubsection{Leadership and alignment}

The importance of leadership in change was described in many sources. Individual
persons as well as task forces and communities acted as change leaders. A factor
related to leadership was creating organizational alignment.
Table \ref{table:success_changeleaders} summarizes factors related to leadership
in change which benefit the transformation.

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Have change leaders  &
                P3, P4, P11, P16, P18, P31, P33, P42  \\
        Have an agile community  &
                P3, P12, P41, P42, P47  \\
        Align the organization  &
                P8, P18, P31, P42, P43, P46  \\
        \bottomrule
    \end{tabular}
    \caption{Success factors relating to leadership in change}
    \label{table:success_changeleaders}
\end{table}

Organizing a large number of people requires some management and leadership.
Similarly, transforming the way of working of a large group requires coordination
and leadership [P31, P42]. In addition to the leadership provided by coaches,
specific change leaders were also mentioned. Cases indicated the importance of
having spokespersons for the change [P3, P4, P31]. Cowan [P11] describes how one
person was strongly driving the transformation, and made an indisputable
contribution for transforming the organization. Also Maples [P31] describes how
the change and agile adoption was guided by one ``counselor'' [P31]. Other cases
described that the change was lead by a competent roll-out team, which had
representatives from all parts of the organization [P16, P33]. Finally, the
responsibility of line and project managers to act as change leaders was
highlighted [P18].

The formation and influence of agile communities was reported to have a
significant impact on transformation.
The emergence of an agile community was reported as a success factor in the
transformation [P3]. A community was also seen as indispensable as it has power
to overcome impediments that would be too large for individuals to affect [P47].
The agile communities achieved to raise awareness of agile methods in the
organization [P41, P42, P47], and spawned eager followers who spread the word
even further [P12].

A factor in achieving change was creating alignment towards the common goal of
introducing new development methods. It was seen as an important factor that all
levels in the organization speak the same language and accept the change [P18,
P31]. Alignment was built by promoting success stories and gathering lists of
problems to tackle [P42, P46]. In one case complete alignment between teams and
within management was considered as necessary to use the agile model in a large
context [P43]. Another case highlighted creating and applying a structured
roll-out process to uniformly introduce agile to a large number of teams [P8].

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Have a pilot project at start  &
                P3, P9, P14, P17, P31, P36, P38, P39, P47  \\
        Gather insights from pilot projects  &
                P8, P22, P27, P40, P45  \\
        \bottomrule
    \end{tabular}
    \caption{Piloting the agile model as a success factor}
    \label{table:success_pilots}
\end{table}

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Customize the agile model to the needs of the organization  &
                P8, P10, P11, P29, P31, P40, P41, P43, P45, P49, P51  \\
        Conformity to a single agile model  &
                P8, P11, P12, P16, P32, P43  \\
        Mapping to the old model eases adaptation  &
                P14, P29, P44, P46, P48  \\
        Keep the new model simple  &
                P5, P10, P16, P40  \\
        \bottomrule
    \end{tabular}
    \caption{Recommendations for choosing the agile model}
    \label{table:success_choosemodel}
\end{table}

@@

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.46\textwidth}
                     >{\raggedright\arraybackslash}p{0.46\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Pay attention to the Product Owner role  &
                P12, P14, P16, P24, P30, P33, P39, P46  \\
        Pay attention to requirements management  &
                P5, P11, P17, P33, P48  \\
        \bottomrule
    \end{tabular}
    \caption{Careful implementation of requirements management seen as a
             success factor}
    \label{table:success_requirements}
\end{table}

@@

Agile methods come as new ways of working to many. In order to get a good start
in the transformation the ideas of the new methods need to be explained
thoroughly. Training sessions are good starting points, but teams should be
accompanied by coaching for a longer time to ensure that the new practices are
learned and applied correctly in practice. Table \ref{table:success_training}
lists references that highlight training and coaching as success factors.

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.46\textwidth}
                     >{\raggedright\arraybackslash}p{0.46\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Providing training on agile methods  &
                P3, P6, P11, P14, P16, P30, P37, P46 \\
        Coaching teams as they learn by doing  &
                P3, P6, P8, P9 P16, P17, P18, P29,
                P30, P33, P42, P44, P47, P48  \\
        \bottomrule
    \end{tabular}
    \caption{Training and coaching presented as success factors}
    \label{table:success_training}
\end{table}

@@

Communication and transparency was an important success factor brought up in the
promary studies. The ongoing change should be communicated intensively to
everyone. Transparency and inclusiveness were success factors related to
communication.
Table \ref{table:success_communication} presents success factors relating to
communicating the change.

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Communicate the change intensively  &
                P16, P22, P33, P40, P41, P43, P48  \\
        Enable transparency in the change  &
                P6, P11, P16, P42, P43  \\
        Engage people broadly in the organization  &
                P4, P6, P16, P22, P31 \\
        \bottomrule
    \end{tabular}
    \caption{Succes factors relating to communicating the change}
    \label{table:success_communication}
\end{table}

@@

Also communicating the goals of the transformation was highlighted in a some
studies.
Having a clear message of expectations helped to remove confusion and make
people understand the purpose of the transformation [P43, P48]. The motivation
to change can be increased by having a simple proposal on how to reach the
desired outcomes [P40].
McDowell and Dourambeis [P32] describe how the organization launched a series of
communications events especially designed to emphasize the reasons behind the
agile practices.

@@

@@

Many cases highlighted the importance of engaging people broadly in the
organization.
One of the lessons learned presented was that it is important to involve all
stakeholders to gain acceptance in the transformation [P4, P31]. The transition
team made an effort to engage people by both inviting to give feedback online
and holding an extensive number of feedback meetings [P6, P16, P22] Being
inclusive towards everyone was seen as one of the key success factors in the
transformation [P16]. Inclusiveness will encourage people to participate and use
the new model visibly [P16].

\subsubsection{Enable autonomy for development teams}

A key principle in agile is to allow development teams decide for themselves how
they execute their tasks. To make te agile model work well teams need to
self-organize, and be allowed to make decisions on the pace of development.
When teams can perform their tasks autonomically the transformation towards
agile will progress.
Table \ref{table:success_autonomy} lists success factors relating to autonomy of
development teams.

\begin{table}[h]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.51\textwidth}
                     >{\raggedright\arraybackslash}p{0.41\textwidth} }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Allow teams to self-organize  &
                P5, P16, P18, P41  \\
        Empower teams to decide over speed and quality  &
                P27, P30, P34, P45  \\
        No top-down mandate  &
                P3, P6, P41  \\
        \bottomrule
    \end{tabular}
    \caption{Success factors relating to enabling autonomy for development teams}
    \label{table:success_autonomy}
\end{table}

@@

Roche and Vasquez-McCall [P41] describe how prescribing the agile methods to use
lead only so-far in the transformation. The effectiveness of teaching and
communicating the transformation started to decline. To enable the
transformation to proceed further, an organization-wide challenge was created
where teams would independently develop and showcase the best agile practices.
As a result the ownership of the methods was transferred to teams, and the new
model gained a secure foothold. [P41]

@@

An interesting success factor was the absence of a top-down mandate. Atlas [P3]
describes that the use of Scrum was spreading because teams were both allowed to
use and enabled to learn the method. The transformation itself was agile when
people felt empowerment in making the decision to adopt. The incentive to change
was created when teams learned about agile methods, and perceived that a change
would be beneficial [P3].
The absence of mandate granted genuine support for the model on the grass roots
level, which was a necessity for the process to work [P6].
It was also thought that proceeding with a top-down mandate would have made
teams conform to a single process [P41]. This would have been sub-optimal, as it
was important that each individual team and project tailored their practices
[P41].

\subsubsection{Choosing the right people}

The transformation did not entirely rely on choices in technology and
management, but also different people factors were given as basis of success.
The choice of people to initially involve in the transformation was reported to
make a difference. Interest or previous experience of agile methods were
valuable characteristics to look for.
Table \ref{table:success_people} lists factors choosing people that can benefit
the transformation.

\begin{table}[h]
    \centering
    \begin{tabular}{ ll }
        \toprule
        Success factors  &  Described in \\
        \midrule
        Start with people who are receptive for agile methods  &
                P6, P29, P34  \\
        Use people with previous agile experience  &
                P6, P10, P37  \\
        Have change leaders without baggage of the past  &
                P11, P16  \\
        \bottomrule
    \end{tabular}
    \caption{Success factors relating to choosing the right people}
    \label{table:success_people}
\end{table}

@@

\subsubsection{Other success factors}

A few succes factors which did not fit in the above categories stood out. These
success factors are creating a positive experience in the beginning, arranging
socaial events, emphasizing principles over mechanics, and the previous
organizational culture being like agile.

@@

In a number of studies it was described that the principles of agile should be
emphasized over practices and simple mechanics [P46, P48]. When people
understand the agile values they will also understand why the change is being
done and feel motivated [P1, P16, P42].
Some cases described that inexperienced coaches and Scrum masters made mistakes
in focusing too much on the implementation of practices [P23, P30].

A few organizations had already some structures in place that were similar to
agile, which made the transformation easier.
For instance, a previous organizational model based on small and autonomous
teams strongly aided the adoption [P3].
Another case described the original on-demand delivery model a natural fit for
agile, and the transformation was presented as a return to core values instead
of a remodeling [P16].
